---
title: "V3_2_CRLM_IHC_wrangling_step2_and_explorative"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Generated on: `r Sys.time()`

```{r }
library(Rmisc)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(caTools)
``` 

```{r }
ihcDataInvPeritFn <- "../out/CRLM_IHC_data_rim_outer_220204_tidied.csv"
ihcDataIntraFn <- "../out/CRLM_IHC_data_intratum_220204_tidied.csv"
#ihcDataDistLongFn <- "../out/CRLM_IHC_data_long.csv"
#ihcDataDistAvgFn <- "../out/CRLM_IHC_data_avg.csv"
```

```{r }
# Read ihc data invperit
ihcDataInvPerit <- read.csv(ihcDataInvPeritFn)
#ihcDataOrig <- ihcDataOrig[ 1:300, ] # temporarily limit dataset size
head(ihcDataInvPerit)

# Read ihc data intratumor
ihcDataIntra <- read.csv(ihcDataIntraFn)
ihcDataIntra <- ihcDataIntra %>% mutate(dist2outer_band = NA)
ihcDataIntra <- ihcDataIntra %>% relocate(dab_mean, .after = tiles_annotation)
head(ihcDataIntra)

colnames(ihcDataInvPerit)
colnames(ihcDataIntra)

# Merge datasets
ihcData <- rbind(ihcDataInvPerit, ihcDataIntra)

# Dimensions of dataset
dim(ihcData)

# Column types
ihcData %>%  summarise(across(everything(), class)) %>% unlist

# Summary of missing data
ihcData %>%  summarise(across(everything(), ~sum(is.na(.x)))) %>% unlist %>% sort(decreasing = T)

# Images
length(levels(ihcData$image))
levels(ihcData$image)

# Markers
levels(ihcData$markers)

# Marker combinations per image
ihcData %>% group_by(image) %>% summarise(marker = unique(markers))

# Number of images per marker combination
ihcData %>% group_by(markers) %>% summarise(count = length(unique(image))) %>% arrange(desc(count))

# List of images per combination
ihcData %>% group_by(markers) %>% summarise(image = unique(image))

# Number of images per dab markers
ihcData %>% group_by(dab_markers) %>% summarise(count = length(unique(image))) %>% arrange(desc(count))

# Number of images per ap markers
ihcData %>% group_by(ap_markers) %>% summarise(count = length(unique(image))) %>% arrange(desc(count))
```

```{r }
# Convert dataset from wide to long by unifying ap and dab markers into markers and ap and dab means into intensity mean
apData <- ihcData %>% select(image, ap_markers, tiles_annotation, dist2inv_front, dist2outer_band, ap_mean)
apData <- apData %>% rename(markers = ap_markers, intensity_mean = ap_mean)

dabData <- ihcData %>% select(image, dab_markers, tiles_annotation, dist2inv_front, dist2outer_band, dab_mean)
dabData <- dabData %>% rename(markers = dab_markers, intensity_mean = dab_mean)

ihcDataLong <- rbind(apData, dabData)
head(ihcDataLong)

# Print combinations of markers and tiles' annotations
ihcDataLong %>% group_by(markers) %>% summarise(tiles_annotation = unique(tiles_annotation))
```

```{r }
# Marker have been quantified for OuterMargiN (peritumoral liver), invasion front (desmoplastic rim) and Intratumor (tumor center) annotations.
# We can then combine dist2outerband (positive for tiles in invasion front) and dist2inv_front (positive for tiles in outer margin and in intratumor)
# into a 'distance' column.

# Desmo rim
ihcDataInvFront <- ihcDataLong %>% filter(tiles_annotation == "Invasion Front") %>% select(image, markers, dist2outer_band, intensity_mean) %>%                                              rename(distance = dist2outer_band) %>% mutate(region = "Desmo rim") # For desmo rim
head(ihcDataInvFront)

# Peritumoral liver
ihcDataOuterMargin <- ihcDataLong %>% filter(tiles_annotation == "OuterMargiN") %>% select(image, markers, dist2inv_front, intensity_mean) %>%                                              rename(distance = dist2inv_front) %>% mutate(region = "Peritumoral liver") # For outer band (peritumoral liver)
ihcDataOuterMargin <- ihcDataOuterMargin %>% filter(distance <= 1500)
head(ihcDataOuterMargin)

# Intratumor
ihcDataIntratumor <- ihcDataLong %>% filter(tiles_annotation == "Tumor") %>% select(image, markers, dist2inv_front, intensity_mean) %>%                                              rename(distance = dist2inv_front) %>% mutate(region = "Tumor center") # For intratumor
head(ihcDataIntratumor)

# Remerge again
ihcDataDistLong <- rbind(ihcDataInvFront, ihcDataOuterMargin)
ihcDataDistLong <- rbind(ihcDataDistLong, ihcDataIntratumor)
head(ihcDataDistLong)

# Recode as '0' negative intensity outliers
ihcDataDistLong <- ihcDataDistLong %>% mutate(intensity_mean = ifelse(intensity_mean < 0, 0, intensity_mean))
```

Fixes after comparison of images with V2 curves
```{r }
# Remove intensities D2-40 > 0.3 (lymphatic endothelium) for T3989, T8292, T4648
filtIhcDataDistLong <- ihcDataDistLong %>% filter(!(image %in% c("T3989-13-A", "T8292-19-C", "T4648-14-1L") & markers == "p53_d240_dab" & intensity_mean > 0.3))
# Remove CD34 values (capillaries) for T3989 (stroma)
filtIhcDataDistLong <- filtIhcDataDistLong %>% filter(!(image == "T3989-13-A" & markers == "p53_cd34_dab"))
# Combine cald_ck19_ap and cald_ck7_ap (ductuli) and remove for T4571-14-K, (mixed with caldesmon str)
filtIhcDataDistLong <- filtIhcDataDistLong %>% mutate(markers = if_else(markers %in% c("cald_ck19_ap", "cald_ck7_ap"), "cald_ck19/ck7_ap", as.character(markers)))
filtIhcDataDistLong <- filtIhcDataDistLong %>% filter(!(image == "T4571-14-K" & markers == "cald_ck19/ck7_ap"))

# After comparison of images with V2 curves: Leave out (do not not plot): cald_masp_ap, cd34_ap, cd146_dab, saa_dab, cald_ck7_dab
filtIhcDataDistLong <- filtIhcDataDistLong %>% filter(!(markers %in% c("cald_masp_ap", "cd34_ap", "cd146_dab", "saa_dab", "cald_ck7_dab")))

# Reorder levels of markers as we want them to be ploted
filtIhcDataDistLong$markers <- factor(filtIhcDataDistLong$markers, levels = c("ngfr_ap", "actinsm_ap", "p53_cd34_dab", "cd68_dab",
                "p53_d240_dab", "cald_ck19/ck7_ap", "ck18_ap",  "ck18_dab", "crp_dab"))
```

```{r }
# Standardize distances from um to % of the band for each combination of image and markers
filtIhcDataDistLong %>% group_by(image, region, markers) %>% summarise(min_dist = min(distance), max_dist = max(distance))

# Do the std distance calculation - interesting, when group_by + mutate, max(d) works in the group, by d on the row
stdIhcDataDistLong <- filtIhcDataDistLong %>% group_by(image, region, markers) %>% mutate(std_distance = 100 / max(distance) * distance)
head(stdIhcDataDistLong)

# For peritumoral liver, keep std dist as is.
# For desmo rim, translate std distace to -100 to 0
stdIhcDataDistLong <- stdIhcDataDistLong %>% mutate(std_distance = ifelse(region == "Desmo rim", -std_distance, std_distance))
stdIhcDataDistLong <- stdIhcDataDistLong %>% mutate(region_part = case_when(
                    region == "Desmo rim" & std_distance < -50 ~ "Inner rim",
                    region == "Desmo rim" & std_distance >= -50 ~ "Outer rim",
                    region != "Desmo rim" ~ region
                    
))
# For tumor center, translate std distace to -200 to -100
stdIhcDataDistLong <- stdIhcDataDistLong %>% mutate(std_distance = ifelse(region == "Tumor center", -std_distance - 100, std_distance))
head(stdIhcDataDistLong)

# Cut std distances into bins
# set up cut-off values 
breaks <- seq(-200, 100, by = 5)
# bucketing values into bins
stdIhcDataDistLong$std_dist_cat <- cut(stdIhcDataDistLong$std_distance, breaks=breaks, include.lowest=TRUE, right=FALSE)

# Obs! Average intensities per distance bin for each image first. Added during revision.
stdIhcDataDistLong2 <- stdIhcDataDistLong %>% group_by(image, markers, region, region_part, std_dist_cat) %>% summarize(intensity_mean = mean(intensity_mean, na.rm = T))
stdIhcDataDistLong <- stdIhcDataDistLong %>% group_by(image, markers, std_dist_cat) %>% summarize(intensity_mean = mean(intensity_mean, na.rm = T))

# inspect bins
summary(stdIhcDataDistLong$std_dist_cat)

# Average intensities with 95% CIs over bins
#avgStdIhcDataDistLong <- stdIhcDataDistLong %>% group_by(markers, std_dist_cat) %>% summarise(intensity_avg = mean(intensity_mean, na.rm = TRUE)) %>% filter(!is.na(std_dist_cat))
avgStdIhcDataDistLong <- stdIhcDataDistLong %>% group_by(markers, std_dist_cat) %>% summarise(intensity_avg = CI(na.omit(intensity_mean), ci = 0.95)["mean"],
                                                                                              intensity_lower = CI(na.omit(intensity_mean), ci = 0.95)["lower"],
                                                                                              intensity_upper = CI(na.omit(intensity_mean), ci = 0.95)["upper"]) %>% filter(!is.na(std_dist_cat)
                                                                                              )
# Calculate the rolling averaged intensity and 95% CIs
# https://stackoverflow.com/questions/70429206/python-calculate-confidence-interval-on-a-rolling-basis
avgStdIhcDataDistLong <- avgStdIhcDataDistLong %>% group_by(markers) %>% arrange (std_dist_cat) %>% mutate(intensity_avg_roll = runmean(intensity_avg, 5, alg = "exact", endrule = "mean", align = "center"),
                                                                                                           intensity_std_roll = runsd(intensity_avg, 5, endrule = "sd", align = "center"),
                                                                                                           intensity_lower_roll = intensity_avg_roll - 1.96 * intensity_std_roll / sqrt(n()),
                                                                                                           intensity_upper_roll = intensity_avg_roll + 1.96 * intensity_std_roll / sqrt(n())
                                                                                                          )

# Average intensities over compartments
avgRegionIhcDataDistLong <- stdIhcDataDistLong2 %>% group_by(image, markers, region) %>% summarise(intensity_avg = mean(intensity_mean, na.rm = TRUE)) %>% filter(!is.na(markers), !is.na(intensity_avg)) # TODO: Where do those NaN come from?
avgRegionIhcDataDistLongV2 <- stdIhcDataDistLong2 %>% group_by(image, markers, region_part) %>% summarise(intensity_avg = mean(intensity_mean, na.rm = TRUE)) %>% filter(!is.na(markers), !is.na(intensity_avg)) # TODO: Where do those NaN come from?
```

Plots v1
```{r }
ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab")), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) + geom_line() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Stroma markers")

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "p53_cd34_dab")), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) + geom_line() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle(paste("Capillaries"))

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "cd68_dab", "ck18_ap", "crp_dab")), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) + geom_line() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle(paste("Hepatocytes and macrofages"))

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "cald_ck19/ck7_ap")), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) + geom_line() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle(paste("Ductuli"))
```

Plots v2
```{r }
invf_perit_dists <- levels(cut(seq(-100,100), breaks= seq(-100, 100, by = 5), include.lowest=TRUE, right=FALSE))
#invf_perit_dists <- invf_perit_dists[0 : (length(invf_perit_dists)-1)]

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab")), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) +
  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="yellow1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=21, xmax=41,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=41, xmax=60,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +  
  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Stroma markers") +
  scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat))

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab")), aes(x = std_dist_cat, y = intensity_avg_roll, group = markers, colour = markers)) +
  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="yellow1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=21, xmax=41,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=41, xmax=60,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +  
  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Stroma markers") +
  scale_x_discrete(breaks = levels(avgStdIhcDataDistLong$std_dist_cat)[c(T, rep(F, 9))])
  #scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat))
  
ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) +
  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=21, xmax=40,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +    
  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Capillaries, macrophages and ductuli") +
  scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat)[21:60])

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg_roll, group = markers, colour = markers)) +
  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=21, xmax=40,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +    
  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Capillaries, macrophages and ductuli") +
  scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat)[21:60])

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ck18_ap", "crp_dab") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) + 
  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=21, xmax=40,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +      
  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Hepatocytes (and ductuli in inv. front)")  +
  scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat)[21:60])

ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ck18_ap", "crp_dab") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg_roll, group = markers, colour = markers)) + 
  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
  geom_rect(aes(xmin=21, xmax=40,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +      
  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Hepatocytes (and ductuli in inv. front)")  +
  scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat)[21:60])
```
Plots v3 - Publication plots
```{r }
# https://www.roelpeters.be/add-confidence-interval-line-ggplot/

#ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg, group = markers, colour = markers)) +
#  geom_rect(aes(xmin=1, xmax=21,ymin=-Inf, ymax=Inf), fill="wheat1", color = NA, alpha = 0.01,  show.legend = FALSE) +
#  geom_rect(aes(xmin=21, xmax=40,ymin=-Inf, ymax=Inf), fill="darkslategray1", color = NA, alpha = 0.01,  show.legend = FALSE) +    
#  geom_line() + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#  geom_ribbon(aes(ymin = intensity_lower, ymax = intensity_upper), alpha = 0.1) +
#  ggtitle("Capillaries, macrophages and ductuli") +
#  scale_x_discrete(limits=levels(avgStdIhcDataDistLong$std_dist_cat)[21:60])

# Fig 5a
ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ck18_ap", "crp_dab") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg_roll, group = markers, colour = markers)) + 
  geom_line() + 
  scale_color_manual(values=c("#e19273", "#86b5da")) +
  geom_ribbon(aes(ymin = intensity_lower_roll, ymax = intensity_upper_roll, fill = markers), alpha = 0.2, linetype="dashed", color="grey") +
  scale_fill_manual(values=c("#e19273", "#86b5da")) +  
  geom_rect(aes(xmin=18.5, xmax=23.5,ymin=-Inf, ymax=Inf), fill="lightgray", color = NA, alpha = 0.02,  show.legend = FALSE) +  
  geom_vline(xintercept = "[0,5)") +
  theme_bw() + theme(
    axis.text.x=element_blank(), axis.ticks.x=element_blank(),
    axis.title.x = element_text(hjust = 0),
    panel.grid.minor.y = element_blank(),
    legend.position = "none"
    ) +
  scale_x_discrete(breaks = c("[-50,-45)", "[50,55)")) +
  xlab("-100%                                                               Interface                                                             100%") + 
  ylab("Average intensity") +
  labs(subtitle = "                                 Fibrotic rim                                                                  Liver") + 
  annotate(geom="text", x=32, y=0.38, label="CK18", size=6, color="#e19273") +
  annotate(geom="text", x=35, y=0.19, label="CRP", size=6, color="#86b5da")
ggsave("plots/Fig 5a.pdf")

# Fig 5d
ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap") & std_dist_cat %in% invf_perit_dists), aes(x = std_dist_cat, y = intensity_avg_roll, group = markers, colour = markers)) +
  geom_line()  + 
  scale_color_manual(values=c("#86b5da", "#e19273", "#99314c")) +
  geom_ribbon(aes(ymin = intensity_lower_roll, ymax = intensity_upper_roll, fill = markers), alpha = 0.2, linetype="dashed", color="grey") +
  scale_fill_manual(values=c("#86b5da", "#e19273", "#99314c")) +  
  geom_rect(aes(xmin=18.5, xmax=23.5,ymin=-Inf, ymax=Inf), fill="lightgray", color = NA, alpha = 0.02,  show.legend = FALSE) +    
  geom_vline(xintercept = "[0,5)") +
  theme_bw() + theme(
    axis.text.x=element_blank(), axis.ticks.x=element_blank(),
    axis.title.x = element_text(hjust = 0),
    panel.grid.minor.y = element_blank(),
    legend.position = "none"
    ) +
  scale_x_discrete(breaks = c("[-50,-45)", "[50,55)")) +
  xlab("-100%                                                              Interface                                                            100%") + 
  ylab("Intensity, rolling average") +
  labs(subtitle = "                                Fibrotic rim                                                                  Liver") +  
  annotate(geom="text", x=32, y=0.125, label="CD34", size=6, color="#86b5da") +
  annotate(geom="text", x=27.7, y=0.09, label="CD68", size=6, color="#e19273") +
  annotate(geom="text", x=25, y=0.013, label="CK7", size=6, color="#99314c")
ggsave("plots/Fig 5d.pdf")

# Fig 6a
ggplot(data = filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "actinsm_ap")), aes(x = std_dist_cat, y = intensity_avg_roll, group = markers, colour = markers)) +
  geom_line() + 
  scale_color_manual(values=c("#e19273", "#86b5da")) +
  geom_ribbon(aes(ymin = intensity_lower_roll, ymax = intensity_upper_roll, fill = markers), alpha = 0.2, linetype="dashed", color="grey") +
  scale_fill_manual(values=c("#e19273", "#86b5da")) +    
  geom_rect(aes(xmin=18.5, xmax=23.5,ymin=-Inf, ymax=Inf), fill="lightgray", color = NA, alpha = 0.02,  show.legend = FALSE) +    
  geom_vline(xintercept = "[-100,-95)") +  
  geom_rect(aes(xmin=38.5, xmax=43.5,ymin=-Inf, ymax=Inf), fill="lightgray", color = NA, alpha = 0.02,  show.legend = FALSE) +    
  geom_vline(xintercept = "[0,5)") +
  theme_bw() + theme(
    axis.text.x=element_blank(), axis.ticks.x=element_blank(),
    axis.title.x = element_text(hjust = 0),
    legend.position = "none"
    ) +
  scale_x_discrete(breaks = c("[-150,-145)", "[-50,-45)", "[50,55)")) +
  xlab("-200%                                     -100%                                        Interface                                   100%") + 
  ylab("Intensity, rolling average") + 
  labs(subtitle = "                       Tumor                                        Fibrotic rim                                       Liver") +
  annotate(geom="text", x=8, y=0.15, label="NGFR", size=6, color="#e19273") +
  annotate(geom="text", x=7.5, y=0.225, label="ASMA", size=6, color="#86b5da")
ggsave("plots/Fig 6a.pdf")
```


Summary stats, boxpPlots and significance between regions for the different markes
```{r }
filtAvgRegionIhcDataDistLong <- avgRegionIhcDataDistLong %>% filter(markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab", "p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap", "ck18_ap", "crp_dab"))
head(filtAvgRegionIhcDataDistLong)

# Shapiro test for normality
filtAvgRegionIhcDataDistLong %>% ungroup() %>% shapiro_test(intensity_avg)

# Summary stats
intensity_descr <- filtAvgRegionIhcDataDistLong %>%
  group_by(markers, region) %>%
  get_summary_stats(intensity_avg, show = c("n", "min", "max", "median"))
intensity_descr

# Significance test: Pairwise Wilcox-test is used because lack of normality
# and Benjamini & Hochberg correction for multiple testing
stat.test <- filtAvgRegionIhcDataDistLong %>%
  group_by(markers) %>%
  pairwise_wilcox_test(
    intensity_avg ~ region) %>%
    adjust_pvalue(method = "BH") %>%
    add_significance("p.adj")
stat.test

# Create the box plots
bxp <- ggboxplot(
  filtAvgRegionIhcDataDistLong, x = "markers", y = "intensity_avg",
  color = "region", palette = "jco"
  )
# Add statistical test p-values
stat.test1 <- stat.test %>% add_xy_position(x = "markers")
bxp + stat_pvalue_manual(label = "p.adj.signif",
  stat.test1, tip.length = 0) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Effect sizes
eff_size <- filtAvgRegionIhcDataDistLong %>%
  group_by(markers) %>%
  wilcox_effsize(
    intensity_avg ~ region, paired = FALSE)
eff_size

# Save datasets
write.csv(filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab", "p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap", "ck18_ap", "crp_dab")), "ihcByDistances.csv", row.names = F)
write.csv(filtAvgRegionIhcDataDistLong, "ihcBySlides.csv", row.names = F)
```

Summary stats V2, boxpPlots and significance between regions for the different markes - leaving out non-stromal markers and analyzing separately inner and out parts of the rim
```{r }
filtAvgRegionIhcDataDistLong <- avgRegionIhcDataDistLongV2 %>% filter(markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab"), region_part != "Peritumoral liver")
filtAvgRegionIhcDataDistLong$markers <- droplevels(filtAvgRegionIhcDataDistLong$markers)
filtAvgRegionIhcDataDistLong$region_part <- as.factor(filtAvgRegionIhcDataDistLong$region_part)
filtAvgRegionIhcDataDistLong$region_part <- fct_relevel(filtAvgRegionIhcDataDistLong$region_part, "Outer rim", "Inner rim", "Tumor center")
head(filtAvgRegionIhcDataDistLong)

# Shapiro test for normality
filtAvgRegionIhcDataDistLong %>% ungroup() %>% shapiro_test(intensity_avg)

# Summary stats
intensity_descr <- filtAvgRegionIhcDataDistLong %>%
  group_by(markers, region_part) %>%
  get_summary_stats(intensity_avg, show = c("n", "min", "max", "median"))
intensity_descr

# Significance test: Pairwise Wilcox-test is used because lack of normality
# and Benjamini & Hochberg correction for multiple testing
stat.test <- filtAvgRegionIhcDataDistLong %>%
  group_by(markers) %>%
  pairwise_wilcox_test(
    intensity_avg ~ region_part) %>%
    adjust_pvalue(method = "BH") %>%
    add_significance("p.adj")
stat.test

# Create the box plots
bxp <- ggboxplot(
  filtAvgRegionIhcDataDistLong, x = "markers", y = "intensity_avg",
  color = "region_part", palette = "jco"
  ) 
# Add statistical test p-values
stat.test1 <- stat.test %>% add_xy_position(x = "markers")
bxp + stat_pvalue_manual(label = "p.adj.signif",
  stat.test1, tip.length = 0) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Effect sizes
eff_size <- filtAvgRegionIhcDataDistLong %>%
  group_by(markers) %>%
  wilcox_effsize(
    intensity_avg ~ region_part, paired = FALSE)
eff_size

# Save datasets
#write.csv(filter(avgStdIhcDataDistLong, markers %in% c("ngfr_ap", "actinsm_ap", "p53_d240_dab", "p53_cd34_dab", "cd68_dab", "cald_ck19/ck7_ap", "ck18_ap", "crp_dab")), "ihcByDistances.csv", row.names = F)
write.csv(filtAvgRegionIhcDataDistLong, "ihcBySlides.csv", row.names = F)
```